\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\PassOptionsToPackage{hyphens}{url}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
% self input packages
\usepackage{academicons}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[normalem]{ulem}
% 定义淡蓝色
\definecolor{lightblue}{rgb}{0.3, 0.6, 0.9}
% 设置页码
\usepackage{fancyhdr}
\usepackage{lipsum} % 用于生成示例文本，可以删除
\pagestyle{fancy}
\fancyhf{} % 清除所有页眉页脚设置
% 设置页码
\fancyfoot[LE,RO]{\thepage}
% LE: 左侧偶数页脚, RO: 右侧奇数页脚
% \thepage 命令用于插入当前页码
% 统一调整字体大小
\usepackage{relsize}
\relsize{40}
\Urlmuskip=0mu plus 1mu
\setlength{\emergencystretch}{2em}
\AtBeginDocument{\hypersetup{breaklinks=true}}
\renewcommand{\underline}[1]{\uline{#1}}


\name{Sichen}{Tao}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\color{gray} \textbf{\\Assistant Professor, \\ High Performance Computing Laboratory, \\ Cyberscience Center, Tohoku University, Japan}\end{center}
\begin{center}
\begin{tabular}{lll}
\faMapMarked*\enspace Sendai-shi, Japan~~~& \faEnvelope\enspace taosc73@hotmail.com/sichen.tao@tohoku.ac.jp~~~& \faPhone\enspace +81-080-4382-4890 \\ \faGraduationCap\enspace \color{black} \href{https://scholar.google.com/citations?user=gmOx-i4AAAAJ&hl=en}{\underline{Google Scholar}~~~~} &
\faResearchgate\enspace \color{black} \href{https://www.researchgate.net/profile/Sichen-Tao}{\underline{ResearchGate (Currently Inaccessible)}} &
\faGithub\enspace \color{black} \href{https://github.com/SichenTao}{\underline{Github}} 
\end{tabular}
\end{center}


\section{Research Interest}
{
- Design and applications of state-of-the-art deep learning technologies.

- Design and applications of state-of-the-art intelligent optimization methods.

- Developing explainable and efficient bio-inspired neural networks for both visual and general cognitive tasks.
}

\section{Education}
\customcventry{2022-2025}{\color{black}\href{https://www.u-toyama.ac.jp/}{\underline{University of Toyama}}}{Doctor of Engineering}{Toyama, Japan}{}{}{Course of Studies: Advanced Mathematics and Human Mechanisms (Artificial Intelligence Lab). \\ Doctoral thesis: ``Development of Artificial Intelligence Systems for Data Analysis and Optimization Based on Brain-inspired and Evolutionary Intelligence".
}

\customcventry{2020-2022}{\color{black}\href{https://www.u-toyama.ac.jp/}{\underline{University of Toyama}}}{Master of Engineering}{Toyama, Japan}{}{}{Course of Studies: Intellectual Information Engineering (Artificial Intelligence Lab). \\ Master thesis: ``A Novel Artificial Visual System for Motion Direction Detection in Grayscale Images".
}

\customcventry{2019-2020}{\color{black}\href{https://www.u-toyama.ac.jp/}{\underline{University of Toyama}}}{Research Student}{Toyama, Japan}{}{}{Course of Studies: Intellectual Information Engineering (Artificial Intelligence Lab). \\ Main Works: Theoretical Researches and Real-World Applications of State-of-the-Art Meta-Heuristic Optimizers.}

\customcventry{2014-2018}{\color{black}\href{https://www.usst.edu.cn/main.htm}{\underline{University of Shanghai for Science and Technology}}}{Bachelor of Engineering}{Shanghai, China}{}{}{Course of Studies: Mechanical Design, Manufacture, and Automation ({\color{orange}\href{https://eurace.enaee.eu/node/7434}{\underline{European Accreditation of Engineering Programmes}, \underline{EUR-ACE\textsuperscript{\textregistered}}}}). 

Bachelor thesis: ``Self-service System Design of Robot Intelligent Restaurant".}

\section{Research and Work Experience}

\customcventry{10/2025 ‐ present}
{}{Assistant Professor}{{\color{black}\href{https://www.tohoku.ac.jp/en/}{\underline{Tohoku University}}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Affiliated with the \color{orange}{\href{https://www.hpc.is.tohoku.ac.jp/home-en/member-en/}{\underline{High Performance Computing Laboratory (Takizawa Laboratory)}}}\color{black}{, }\color{orange}{\href{https://www.cc.tohoku.ac.jp/english/}{\underline{Cyberscience Center}}}.
\end{itemize}}}

\customcventry{04/2023 ‐ 9/2025}
{}{JST SPRING Researcher}{{\color{black}\href{https://www.jst.go.jp/EN/}{\underline{Japan Science and Technology Agency}}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Researches are supported by \color{orange}\href{https://www.jst.go.jp/jisedai/spring/en/index.html}{\underline{Japan Science and Technology Agency (JST) Support for Pioneering Research Initiated by the} \\ 
\underline{Next Generation (SPRING)}}.
\end{itemize}}}

\customcventry{03/2023 ‐ 09/2025}
{}{Editor Assistant}{{\color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics}}}, MDPI}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Assist each editor of the special issue ``{\color{orange}\href{https://www.mdpi.com/journal/mathematics/special_issues/dynamics_neural_networks}{\underline{Dynamics in Neural Networks}}}" with initial manuscript review, assigning reviewers, reactivating reviews, and making final decisions.\\
\end{itemize}}}

\customcventry{05/2023 ‐ 1/2025}
{}{Editor Assistant}{{\color{black}\href{https://www.frontiersin.org/journals/neuroscience}{\underline{{Frontiers in Neuroscience}}}}, Frontiers}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Assist each editor of the special issue ``{\color{orange}\href{https://www.frontiersin.org/research-topics/57138/artificial-systems-based-on-human-and-animal-natural-vision-in-image-and-video/overview}{\underline{Artificial Systems Based on Human and Animal Natural Vision in Image and Video}}}" with initial manuscript review, assigning reviewers, reactivating reviews, and making final decisions.\\
\end{itemize}}}

\customcventry{10/2022 ‐ 09/2025}
{}{Research Assistant}{AI Laboratory, \color{black}\href{https://www.u-toyama.ac.jp/}{\underline{University of Toyama}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Assist the professor in leading master's and PhD students to advance research projects, reviewing papers, and holding the seminar.\\
\end{itemize}}}

\customcventry{10/2022 ‐ 03/2024}
{}{JST Fellowship Researcher}{{\color{black}\href{https://www.jst.go.jp/EN/programs/PE.html}{\underline{Japan Science and Technology Agency}}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Researches are supported by {\color{orange}\href{https://www.jst.go.jp/EN/programs/PE.html}{\underline{Japan Science and Technology Agency (JST) through the Establishment of University Fellowships} \\ \underline{towards the Creation of Science Technology Innovation}}} and {\color{orange}\href{https://promotion-research.ctg.u-toyama.ac.jp/fellowship-students/}{\underline{University of Toyama through Fellowships to Create Science, Tech-} \\ \underline{nology and Innovation}}}.\\
\end{itemize}}}

\customcventry{12/2022 ‐ 12/2022}
{}{Research Visit}{Department of Physiology, \color{black}\href{https://www.u-tokyo.ac.jp/ja/index.html}{\underline{University of Tokyo}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Discuss the potential research and collaboration of our proposed motion direction and orientation perception neural modeling in explaining and modeling the mammalian physiological visual system.\\
\end{itemize}}}

\customcventry{10/2020 ‐ 9/2022}
{}{Teaching Assistant}{AI Laboratory, \color{black}\href{https://www.u-toyama.ac.jp/}{\underline{University of Toyama}}}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Assist the professor in teaching and give research-related lectures to undergraduates.
\end{itemize}}}

\section{Publications \& Presentations (52 Items)}
\subsection{\textcolor{lightblue}{PEER-REVIEWED JOURNAL PUBLICATIONS}}
\textcolor{orange}{*Corresponding Author}
{\begin{itemize}[label=\textbullet]

      \item [36)] R. Zhao, J. Betz, \textbf{S. Tao}, Y. Zhang, P. Li, “Neurophysiological Knowledge Driven Artificial Visual System Neural Network for Explainable Motion Direction Detection”, \color{black}\href{https://www.sciencedirect.com/journal/knowledge-based-systems}{\underline{Knowledge-Based Systems (IF=7.6, JCR Q1)}}, 2025, Submitted.
      
      \item [35)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, R. Zhao, Z. Lei, M. Omura, S. Gao, “Level-Direction Guided Hierarchical Genetic Learning Particle Swarm Optimization for Wind Farm Layout Optimization Considering Landowners Behavior”, \color{black} \href{https://www.sciencedirect.com/journal/engineering-applications-of-artificial-intelligence}{\underline{Engineering Applications }\\\underline{of Artificial Intelligence (IF=8.0, JCR Q1)}}, Under Review.
      
      \item [34)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, R. Zhao, H. Yang, J. Wang, “An Artificial Visual System Constructed by Fully Modeled Retinal Direction-selective Networks on Detecting Motion Direction in Color Images”, \color{black}\href{https://www.sciencedirect.com/journal/information-sciences}{\underline{Information Sciences (IF=6.8, JCR Q1)}}, Submitted.
      
      \item [33)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, Y. Yang, R. Zhao, Z. Lei, S. Gao, “Unleashing the Inherent Potential of Differential Evolution Using Nonlinear Population Size Reduction for Wind Farm Layout Optimization”, \color{black}\href{https://ieeeaccess.ieee.org/}{\underline{IEEE Access (IF=3.4, JCR Q1)}}, Under Review.
      
      \item [32)] R. Zhao, \textbf{S. Tao}, P. Li, “Adaptive product family formation: A medoid-based fuzzy clustering method for mixed products assembly in the shared human-robot collaborative system”, \href{https://www.sciencedirect.com/journal/applied-soft-computing}{\underline{Applied Soft Computing (IF=6.6, JCR Q1)}}, Under Review.

      \item [31)] G. Luo, X. Wang, W. Zhao, \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, Z. Tang, “ReLU Neural Networks and Their Training,” \color{black}\href{https://doi.org/10.3390/math14010039}{\underline{Mathematics (IF=2.2, JCR Q1)}}, 2026, 14(1), 39.

      \item [30)] C. Li, Q. Zhang, J. Li, \textbf{S. Tao}, D. Oliva, “Adversarial game optimization: A game-theoretic metaheuristic for efficient complex optimization and engineering applications,” \color{black}\href{https://doi.org/10.1016/j.ins.2025.123022}{\underline{Information Sciences (IF=6.8, JCR Q1)}}, Available online 20 Dec. 2025, 123022 (in press).
      
      \item [29)] Y. Wang, Y. Yang, \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, L. Qi, H. Shen, “A Reinforcement Learning-Assisted Fractional-Order Differential Evolution for Solving Wind Farm Layout Optimization Problems,” \color{black}\href{https://doi.org/10.3390/math13182935}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 13, no. 18, 2935, Sep. 10, 2025.

      \item [28)] Q. Zhang, W. Chen, S. Pang, \textbf{S. Tao}, C. Li, X. Yin, “GPU/CUDA-Accelerated Gradient Growth Optimizer for Efficient Complex Numerical Global Optimization,” \color{black}\href{https://doi.org/10.1016/j.parco.2025.103160}{\underline{Parallel Computing (IF=2.1, JCR Q2)}}, vol. 126, 103160, Nov. 2025.

      \item [27)] R. Zhao, \textbf{S. Tao}, P. Li, “Human-centric Assembly Planning Framework for Human-robot Collaborative Systems with Efficient Reinforcement Self-learning Multi-objective Evolutionary Optimizer”, \color{black}\href{https://www.sciencedirect.com/journal/advanced-engineering-informatics}{\underline{Advanced Engineering Informatics (IF=9.9, }\\\underline{JCR Q1)}}, vol. 67, no. 103508, Sep. 2025, doi: 10.1016/j.aei.2025.103508.
      
      \item [26)] S. Liu, \textbf{S. Tao}, K. Wang, Z. Lei, and S. Gao, “Improved spherical search algorithm with memory-based dynamic population for optimization”, \color{black}\href{https://link.springer.com/journal/11227}{\underline{The Journal of Supercomputing (IF=2.5, JCR Q2)}}, vol. 81, no. 726, Apr. 2025, doi: 10.1007/s11227-025-07095-z.
      
      \item [25)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, S. Liu, S. Ohta, R. Zhao, Z. Tang, and Y. Yang, “A Novel Detection-and-Replacement-Based Order-Operator for Differential Evolution in Solving Complex Bound Constrained Optimization Problems”, \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 13, no. 9, p. 1389, May 2025, doi: 10.3390/math13091389.

      \item [24)] S. Wang, \textbf{S. Tao \textcolor{orange}{(Co-first Author)}}, Y. Zhu, Q. Gu, P. Ni, W. Zhang, C. Wu, R. Zhao, W. Hu, and M. Diao, “AI-powered model for predicting mortality risk in VA-ECMO patients: a multicenter cohort study”, \color{black}\href{https://www.nature.com/srep/}{\underline{Scientific Reports (IF=3.8, JCR Q1)}}, vol. 15, no. 10362, Mar. 2025, doi: 10.1038/s41598-025-94734-3. 
            
      \item [23)] Y. Hua, \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, Y. Todo, T. Chen, Z. Qiu, and Z. Tang, “A Biologically Inspired Model for Detecting Object Motion Direction in Stereoscopic Vision”, \color{black}\href{https://www.mdpi.com/journal/symmetry}{\underline{Symmetry (IF=2.2, JCR Q2)}}, vol. 17, no. 2, p. 162, Jan. 2025, doi: 10.3390/sym17020162.
      
      \item [22)] B. Li, Y. Todo, \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, C. Tang, and Y. Wang, “Enhancing Convolutional Neural Network Robustness Against Image Noise via an Artificial Visual System”, \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 13, no. 1, p. 142, Jan. 2025, doi: 10.3390/math13010142.
      
      \item [21)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, S. Liu, R. Zhao, Y. Yang, H. Todo, and H. Yang, “A State-of-the-Art Fractional Order-Driven Differential Evolution for Wind Farm Layout Optimization”, \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 13, no. 2, p. 282, Jan. 2025, doi: 10.3390/math13020282.
      
      \item [20)] R. Zhao, \textbf{S. Tao}, and P. Li, “Safety-efficiency integrated assembly: The next-stage adaptive task allocation and planning framework for human–robot collaboration”, \color{black}\href{https://www.sciencedirect.com/journal/robotics-and-computer-integrated-manufacturing}{\underline{Robotics and Computer-Integrated Manufacturing (IF=11.4, JCR Q1)}}, vol. 94, Aug. 2025, p. 102942, doi: 10.1016/j.rcim.2024.102942.
      
      \item [19)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, R. Zhao, Y. Yang, H. Todo, Z. Tang, Y. Todo, “Artificial Visual Network with Fully Modeled Retinal Direction-Selective Neural Pathway for Motion Direction Detection in Grayscale Scenes”, \color{black}\href{https://www.mdpi.com/journal/symmetry}{\underline{Symmetry (IF=2.2, JCR Q2)}}, vol. 16, no. 12, p. 1592, Nov. 2024, doi: 10.3390/sym16121592.
      
      \item [18)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, Y. Yang, R. Zhao, H. Todo, Z. Tang, “Competitive Elimination Improved Differential Evolution for Wind Farm Layout Optimization Problems”, \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 12, no. 23, p. 3762, Nov. 2024, doi: 10.3390/math12233762.
      
      \item [17)] Y. Yang, \textbf{S. Tao \textcolor{orange}{(Co-first Author)}}, H. Li, H. Yang, Z. Tang, “A Multi-Local Search-Based SHADE for Wind Farm Layout Optimization”, \color{black}\href{https://www.mdpi.com/journal/electronics}{\underline{Electronics (IF=2.6, JCR Q2)}}, vol. 13, no. 16, p. 3196, Aug. 2024, doi: 10.3390/electronics13163196.
      
      \item [16)] Y. Hua, Y. Todo, \textbf{S. Tao}, Z. Tang, T. Chen, and Z. Qiu, “Bio-inspired computational model for direction and speed detection”, \color{black}\href{https://www.sciencedirect.com/journal/knowledge-based-systems}{\underline{Knowledge-Based Systems (IF=7.2, JCR Q1)}}, vol. 300, p. 112195, Sep. 2024, doi: 10.1016/j.knosys.2024.112195.
      
      \item [15)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, Z. Zhang, R. Zhao, Z. Tang, and Y. Todo, “A novel artificial visual system for motion direction detection in color images,” \color{black}\href{https://www.sciencedirect.com/journal/knowledge-based-systems}{\underline{Knowledge-Based Systems (IF=8.8, JCR Q1)}}, vol. 295, p. 111816, Jul. 2024, doi: 10.1016/j.knosys.2024.111816.
      
      \item [14)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, K. Wang, T. Jin, Z. Wu, Z. Lei, and S. Gao, “Spherical Search Algorithm with Memory-Guided Population Stage-Wise Control for Bound-Constrained Global Optimization Problems,” \color{black}\href{https://www.sciencedirect.com/journal/applied-soft-computing}{\underline{Applied Soft Computing (IF=8.7}, \\ \underline{JCR Q1)}}, vol. 161, p. 111677, Aug. 2024, doi: 10.1016/j.asoc.2024.111677.

      \item [13)] Y. Yang, \textbf{S. Tao}, S. Dong, M. Nomura, and Z. Tang, “An Adaptive Dimension Weighting Spherical Evolution to Solve Continuous Optimization Problems,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 11, no. 17, p. 3733, Aug. 2023, doi: 10.3390/math11173733. 
      
      \item [12)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, X. Zhang, Y. Hua, Z. Tang, and Y. Todo, “A Novel Artificial Visual System for Motion Direction Detection with Completely Modeled Retinal Direction-Selective Pathway,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 11, no. 17, p. 3732, Aug. 2023, doi: 10.3390/math11173732.
      
      \item [11)] Z. Tang, K. Wang, \textbf{S. Tao}, Y. Todo, RL. Wang, and S. Gao, “Hierarchical Manta Ray Foraging Optimization with Weighted Fitness-Distance Balance Selection,” \color{black}\href{https://link.springer.com/journal/44196}{\underline{International Journal of Computational Intelligence Systems (IF=2.9, JCR Q3)}}, vol. 16, no. 114, Jul. 2023, doi: 10.1007/s44196-023-00289-4.

      \item [10)] Y. Yang, \textbf{S. Tao}, H. Yang, Z. Yuan, and Z. Tang, “Dynamic Complex Network, Exploring Differential Evolution Algorithms from Another Perspective,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 11, no. 13, p. 2979, July 2023, doi: 10.3390/math11132979.
      
      \item [9)] X. Zhang, \textbf{S. Tao}, Z. Tang, S. Zheng, and Y. Todo, “The Mechanism of Orientation Detection Based on Artificial Visual System for Greyscale Images,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 11, no. 12, p. 2715, Jun. 2023, doi: 10.3390/math11122715.
      
      \item [8)] K. Wang, Y. Wang, \textbf{S. Tao}, Z. Cai, Z. Lei, and S. Gao, “Spherical Search Algorithm with Adaptive Population Control for Global Continuous Optimization Problems,” \color{black}\href{https://www.sciencedirect.com/journal/applied-soft-computing}{\underline{Applied Soft Computing (IF=8.7, JCR Q1)}}, vol. 132, p. 109845, Jan. 2023, doi: 10.1016/j.asoc.2022.109845.
      
      \item [7)] Y. Hua, Y. Todo, Z. Tang, \textbf{S. Tao}, B. Li, and R. Inoue, “A Novel Bio-Inspired Motion Direction Detection Mechanism in Binary and Grayscale Background,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 10, no. 20, p. 3767, Oct. 2022, doi: 10.3390/math10203767.
      
      \item [6)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, Y. Todo, Z. Tang, B. Li, Z. Zhang, and R. Inoue, “A Novel Artificial Visual System for Motion Direction Detection in Grayscale Images,” \color{black}\href{https://www.mdpi.com/journal/mathematics}{\underline{Mathematics (IF=2.3, JCR Q1)}}, vol. 10, no. 16, p. 2975, Aug. 2022, doi: 10.3390/math10162975.
      
      \item [5)] Z. Tang, \textbf{S. Tao}, K. Wang, B. Lu, Y. Todo, and S. Gao, “Chaotic Wind Driven Optimization with Fitness Distance Balance Strategy,” \color{black}\href{https://link.springer.com/journal/44196}{\underline{International Journal of Computational Intelligence Systems (IF=2.9, JCR Q3)}}, vol. 15, no. 46, Jul. 2022, doi: 10.1007/s44196-022-00099-0.
      
      \item [4)] X. Li, K. Wang, H. Yang, \textbf{S. Tao}, S. Feng, and S. Gao, “PAIDDE: A Permutation-Archive Information Directed Differential Evolution Algorithm,” IEEE Access, vol. 10, pp. 50384-50402, May 2022, doi: 10.1109/ACCESS.2022.3173622.
      
      \item [3)] H. Yang, \textbf{S. Tao}, Z. Zhang, Z. Cai, and S. Gao, “Spatial Information Sampling: Another Feedback Mechanism of Realising Adaptive Parameter Control in Meta-Heuristic Algorithms,” \color{black}\href{https://www.inderscience.com/jhome.php?jcode=ijbic}{\underline{International Journal of Bio-Inspired Computation (IF=1.9, JCR Q2)}}, vol. 19, no. 1, pp. 48-58, Feb. 2022, doi: 10.1504/IJBIC.2022.120751.
      
      \item [2)] K. Wang, \textbf{S. Tao}, R.-L. Wang, Y. Todo, and S. Gao, “Fitness-Distance Balance with Functional Weights: A New Selection Method for Evolutionary Algorithms,” IEICE Transactions on Information and Systems, vol. E104-D, no. 10, pp. 1789-1792, Oct. 2021, doi: 10.1587/transinf.2021EDL8033.
      
      \item [1)] S. Gao, K. Wang, \textbf{S. Tao \color{orange}{(Clarivate 2021 ESI Highly Cited Paper, Top 1\%)}}, T. Jin, H. Dai, and J. Cheng, “A State-of-the-Art Differential Evolution Algorithm for Parameter Estimation of Solar Photovoltaic Models,” \color{black}\href{https://www.sciencedirect.com/journal/energy-conversion-and-management}{\underline{Energy Conversion }\\\underline{and Management (IF=10.4, JCR Q1)}}, vol. 230, p. 113784, Feb. 2021, doi: 10.1016/j.enconman.2020.113784. 

  \end{itemize}} 

\subsection{\textcolor{lightblue}{PEER-REVIEWED CONFERENCE PUBLICATIONS}}
\textcolor{orange}{*Corresponding Author}
% \customcventry{}{\color{black}\href{}{}}{}{}{}{\textcolor{orange}{*Corresponding Author}}{}
{\begin{itemize}[label=\textbullet]


      \item [15)] X. Pan, Y. Shimomura, \textbf{S. Tao}, M. Kawai, K. Takahashi, H. Takizawa, “CityScaleCast: Spatiotemporal GNN for City-Scale Weather Prediction with GraphCast-Guided Parallel Modeling and Multi-Step Forecasting in Sendai,” \color{black}\href{https://doi.org/}{\underline{SCA/HPCAsiaWS 2026 (SCA/HPCAsia 2026 Workshops)}}, Osaka, Japan, Jan. 26–29, 2026 (accepted).
      
      \item [14)] R. Zhao, \textbf{S. Tao}, P. Li, “Human-robot Collaborative Resource and Task Planning for Assembly Systems with Self-learning Multi-objective Evolutionary Optimizer”, \color{black}\href{https://ieeexplore.ieee.org/xpl/conhome/11139128/proceeding}{\underline{IEEE International Conference on Real-time Computing and Robotics (RCAR)}}, Toyama, Japan, Jun. 1–6, 2025, doi:10.1109/RCAR65431.2025.11139773.
            
      \item [13)] Y. Hua, Y. Todo, \textbf{S. Tao}, T. Chen, Z. Qiu, M. Dong, and Z. Tang, “A bio-inspired model for object motion direction and speed detection against colored backgrounds”, in \color{black}\href{https://doi.org/10.1117/12.3056633}{Proceedings of the 5th International Conference on Computer Vision and Information Technology (CVIT 2024)}, vol. 13443, p. 1344307, Dec. 2024, Beijing, China, doi: 10.1117/12.3056633.


      \item[12)] S. Sun, R. Zhao, C. Wang, Z. Tang, and \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, “Improving the Music Harmony Search Using a Differential Exploration Phase for Solving Bound Constrained Optimization Problems,” in \textit{2024 IEEE 7th Information Technology, Networking, Electronic and Automation Control Conference (ITNEC)}, Sep. 2024, doi: \href{https://doi.org/10.1109/ITNEC60942.2024.10733307}{10.1109/ITNEC60942.2024.10733307}.
 
      
      \item [11)] S. Sun, R. Zhao, C. Wang, Z. Tang, and \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, “A Differential Search Integrated Music Harmony Search Algorithm for Solving Bound Constrained Optimization Problems,” in \textit{SPML '24: Proceedings of the 2024 7th International Conference on Signal Processing and Machine Learning}, Oct. 2024, pp. 231-235, doi: \href{https://doi.org/10.1145/3686490.3686524}{10.1145/3686490.3686524}.
      
      \item [10)] Y. Shoji, \textbf{S. Tao\textcolor{orange}{* (Corresponding Author)}}, Y. Todo, Z. Tang, and R. Zhao, “A Novel Artificial Visual System with Fully Modeled Retinal Direction-selectivity Ganglion Cell Pathway for Motion Direction Detection in Grayscale Images,” in \textit{SPML '24: Proceedings of the 2024 7th International Conference on Signal Processing and Machine Learning}, Oct. 2024, pp. 212-215, doi: \href{https://doi.org/10.1145/3686490.3686521}{10.1145/3686490.3686521}.
      
      \item [9)] R. Zhao, \textbf{S. Tao}, and P. Li, “An Optimal-Parent-Crossover based Differential Evolution,” in 2022 15th International Symposium on Computational Intelligence and Design (ISCID), Hangzhou, China, Dec. 2022, doi: 10.1109/ISCID56505.2022.00068.
      
      \item [8)] Q. Sui, \textbf{S. Tao}, L. Zhong, H. Yang, Z. Lei, and S. Gao, “An Immigration Strategy-Based Spherical Search Algorithm,” in 2022 IEEE International Conference on Networking, Sensing and Control (ICNSC), Shanghai, China, Dec. 2022, doi: 10.1109/ICNSC55942.2022.10004149.
      
      \item [7)] L. Zhong, \textbf{S. Tao}, Q. Sui, H. Yang, Z. Lei, and S. Gao, “A Population Resource Allocation-Based Adaptive Spherical Search Algorithm,” in 2022 IEEE International Conference on Networking, Sensing and Control (ICNSC), Shanghai, China, Dec. 2022, doi: 10.1109/ICNSC55942.2022.10004116.
      
      \item [6)] S. Dong, H. Yang, H. Li, B. Zhang, \textbf{S. Tao}, and S. Gao, “Hierarchical Water Wave Optimization,” in 2022 IEEE International Conference on Networking, Sensing and Control (ICNSC), Shanghai, China, Dec. 2022, doi: 10.1109/ICNSC55942.2022.10004174.
      
      \item [5)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author)}}, R. Inoue, Y. Todo, and Z. Tang, “A Motion Direction Detective Mechanism for Greyscale Images,” in Proceedings of the 2021 4th International Conference on Signal Processing and Machine Learning (SPML), Aug. 2021, pp. 18-25, doi: 10.1145/3483207.3483211.
      
      \item [4)] Z. Tang, K. Wang, J. Shi, \textbf{S. Tao}, Y. Todo, and S. Gao, “A Novel Optimization Algorithm Inherited from Gravitational and Spherical Search Dynamics,” in 2020 13th International Symposium on Computational Intelligence and Design (ISCID), Hangzhou, China, Dec. 2020, doi: 10.1109/ISCID51228.2020.00027.
      
      \item [3)] S. Liu, \textbf{S. Tao}, H. Yang, L. Jiang, Y. Todo, and S. Gao, “Using Grey Wolf Hunting Mechanism to Improve Spherical Search,” in 2020 13th International Symposium on Computational Intelligence and Design (ISCID), Hangzhou, China, Dec. 2020, doi: 10.1109/ISCID51228.2020.00022.
      
      \item [2)] K. Wang, \textbf{S. Tao}, Z. Zhang, Y. Todo, and S. Gao, “A Hybrid Spherical Search and Sine Cosine Algorithm,” in 2020 12th International Conference on Intelligent Human-Machine Systems and Cybernetics (IHMSC), Hangzhou, China, Aug. 2020, doi: 10.1109/IHMSC49165.2020.00053.
      
      \item [1)] \textbf{S. Tao \textcolor{orange}{(First Author)}}, K. Wang, Z. Zhang, C. Lee, Y. Todo, and S. Gao, “A Hybrid Spherical Search and Moth-Flame Optimization Algorithm,” in 2020 12th International Conference on Intelligent Human-Machine Systems and Cybernetics (IHMSC), Hangzhou, China, Aug. 2020, doi: 10.1109/IHMSC49165.2020.00054.

  \end{itemize}} 

\subsection{\textcolor{lightblue}{OTHER PUBLICATIONS}}

{\begin{itemize}[label=\textbullet]
    \item [1)] \textbf{S. Tao\textcolor{orange}{* (Corresponding Author \& First Author \& Silver Awardee in Competition on IEEE WCCI 2024)}}, R. Zhao, K. Wang, and S. Gao, “An Efficient Reconstructed Differential Evolution Variant by Some of the Current State-of-the-Art Strategies for Solving Single Objective Bound Constrained Problems,” arXiv, Apr. 25, 2024, doi: 10.48550/arXiv.2404.16280. ({\color{orange}{Silver Awardee in \href{https://2024.ieeewcci.org/program/competitions}{\underline{IEEE CEC2024 Competition on Numerical Optimization}} under \href{https://2024.ieeewcci.org/}{\underline{The IEEE World Congress on Computational Intelligence (IEEE WCCI 2024)}}}})
\end{itemize}

% \section{Honors and Awards}
% \begin{tabular}{>{\raggedright}p{5cm} p{15cm}}
% % \textbf{\textcolor{lightblue}{06/2025}} & \color{orange}{Champion Awardee} \color{black}{in Competition on Constrained Multi-Objective Optimization} \\& 
% % \color{orange}{Champion Awardee} \color{black}{in Competition on Bound-Constrained Multi-Objective Optimization} \\& 
% % \color{orange}{Champion Awardee} \color{black}{in Competition on Constrained Singe-Objective Optimization} \\& 
% % \color{orange}{Silver Awardee} \color{black}{in Competition on Bound-Constrained Single-Objective Optimization} \\& 
% % in \color{orange}{\href{https://www.cec2025.org/}{\underline{The IEEE World Congress on Evolutionary Computation (IEEE CEC 2025)}}}\\

% \textbf{\textcolor{lightblue}{06/2024}} & \color{orange}{Silver Awardee} \color{black}{in Competition on Numerical Optimization Special Session} \\& in \color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE World Congress on Computational Intelligence (IEEE WCCI 2024)}}}\\

% \textbf{\textcolor{lightblue}{04/2023}} & Japan Science and Technology Agency (JST) SPRING Ph.D Full Scholarship Awardee for \\&University of Toyama\\

% \textbf{\textcolor{lightblue}{10/2022}} & Japan Science and Technology Agency (JST) Fellowship Ph.D Full Scholarship Awardee \\&for University of Toyama\\

% \textbf{\textcolor{lightblue}{10/2022}} & Japan NIKKI Foundation Scholarship Awardee\\

% \textbf{\textcolor{lightblue}{10/2021}} & Japan ASAHI Foundation International Communication Scholarship Awardee\\
% \end{tabular}

\section{Honors and Awards}
\subsection{\textcolor{lightblue}{06/2025}}
{\begin{itemize}[label=\textbullet]
      \item [(9)] \color{orange}{\textbf{Champion Awardee}} \color{black}{in Competition on \textbf{Bound-constrained Single-Objective} Numerical Optimization Special Session in }\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE International Congress on Evolutionary Computation (IEEE CEC 2025)}}}\color{black}{.}
      
      \item [(8)] \color{orange}{\textbf{Champion Awardee}} \color{black}{in Competition on \textbf{Variable-Constrained Single-Objective} Numerical Optimization Special Session in }\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE International Congress on Evolutionary Computation (IEEE CEC 2025)}}}\color{black}{.}
      
      \item [(7)] \color{orange}{\textbf{Champion Awardee}} \color{black}{in Competition on \textbf{Bound-Constrained Multi-Objective} Numerical Optimization Special Session in }\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE International Congress on Evolutionary Computation (IEEE CEC 2025)}}}\color{black}{.}
      
      \item [(6)] \color{orange}{\textbf{Champion Awardee}} \color{black}{in Competition on \textbf{Variable-Constrained Multi-Objective} Numerical Optimization Special Session in }\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE International Congress on Evolutionary Computation (IEEE CEC 2025)}}}\color{black}{.}
  \end{itemize}}
  
\subsection{\textcolor{lightblue}{06/2024}}
{\begin{itemize}[label=\textbullet]
      \item [(5)] \color{orange}{\textbf{Silver Awardee}} \color{black}{in Competition on Numerical Optimization Special Session in }\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{The IEEE World Congress on Computational }}}\\\color{orange}{\href{https://2024.ieeewcci.org/}{\underline{Intelligence (IEEE WCCI 2024)}}}\color{black}{.}
  \end{itemize}}
  
\subsection{\textcolor{lightblue}{04/2023}}
{\begin{itemize}[label=\textbullet]
      \item [(4)] \color{orange}{\textbf{Fellowship Awardee}\color{black}{ of }}\color{orange}{\href{https://www.jst.go.jp/EN/}{\underline{Japan Science and Technology Agency (JST)}}}\color{black}{ : }\color{orange}{\href{https://www.jst.go.jp/jisedai/spring/en/index.html}{\underline{Support for Pioneering Research Initiated by }}}\\\color{orange}{\href{https://www.jst.go.jp/jisedai/spring/en/index.html}{\underline{the Next Generation (SPRING)}}}\color{black}{.}
  \end{itemize}}
  
\subsection{\textcolor{lightblue}{10/2022}}
{\begin{itemize}[label=\textbullet]
      \item [(3)] \color{orange}{\textbf{Fellowship Awardee}}\color{black}{ of }\color{orange}{\href{https://www.jst.go.jp/EN/}{\underline{Japan Science and Technology Agency (JST)}}}\color{black}{ : }\color{orange}{\href{https://www.jst.go.jp/EN/programs/PE.html}{\underline{Establishment of University Fellowships towards }}}\\\color{orange}{\href{https://www.jst.go.jp/EN/programs/PE.html}{\underline{the Creation of Science Technology Innovation}}}\color{black}{.}
  \end{itemize}}
  
\subsection{\textcolor{lightblue}{10/2022}}
{\begin{itemize}[label=\textbullet]
      \item [(2)] \color{orange}{\textbf{Scholarship Awardee}}\color{black}{ of }\color{orange}{\href{https://www.jgcs.or.jp/}{\underline{Japan JGC-S Scholarship Foundation}}}\color{black}{.}
  \end{itemize}}
  
\subsection{\textcolor{lightblue}{10/2021}}
{\begin{itemize}[label=\textbullet]
      \item [(1)] \color{orange}{\textbf{Scholarship Awardee}}\color{black}{ of }\color{orange}{\href{https://www.asahi-fie.com/}{\underline{Japan ASAHI International Education Foundation}}}\color{black}{.}
  \end{itemize}}

  

% \textbf{\textcolor{lightblue}{04/2023}} & Japan Science and Technology Agency (JST) SPRING Ph.D Full Scholarship Awardee for \\&University of Toyama\\

% \textbf{\textcolor{lightblue}{10/2022}} & Japan Science and Technology Agency (JST) Fellowship Ph.D Full Scholarship Awardee \\&for University of Toyama\\

% \textbf{\textcolor{lightblue}{10/2022}} & Japan NIKKI Foundation Scholarship Awardee\\

% \textbf{\textcolor{lightblue}{10/2021}} & Japan ASAHI Foundation International Communication Scholarship Awardee\\

\section{Service to Academic Community}
\subsection{\textcolor{lightblue}{REVIEW ACTIVITIES}}
{\begin{itemize}[label=\textbullet]
      \item {\color{orange}\href{https://2024.ieeewcci.org/}{\underline{The IEEE World Congress on Computational Intelligence (IEEE WCCI 2024)}}}
      \item {\color{orange}\href{https://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=4235}{\underline{IEEE Transactions on Evolutionary Computation (IF: 11.7, JCR Q1)}}}
      \item {\color{orange}\href{https://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=6221021}{\underline{IEEE Transactions on Systems, Man and Cybernetics: Systems (IF: 8.7, JCR Q1)}}}
      \item {\color{orange}\href{https://2024.ieeewcci.org/}{\underline{IEEE Congress on Evolutionary Computation (IEEE CEC 2024)}}}
      \item {\color{orange}\href{https://www.cec2025.org/index/page.html?id=1302}{\underline{IEEE Congress on Evolutionary Computation (IEEE CEC 2025)}}}
      \item {\color{orange}\href{https://www.ieeesmc2024.org/home}{\underline{IEEE International Conference on Systems, Man, and Cybernetics (IEEE SMC 2024)}}}
      \item {\color{orange}\href{https://www.sciencedirect.com/journal/swarm-and-evolutionary-computation}{\underline{(Elsevier) Swarm and Evolutionary Computation (IF: 8.2, JCR Q1)}}}
      \item {\color{orange}\href{https://www.sciencedirect.com/journal/engineering-applications-of-artificial-intelligence}{\underline{(Elsevier) Engineering Applications of Artificial Intelligence (IF: 8.0, JCR Q1)}}}
      \item {\color{orange}\href{https://www.sciencedirect.com/journal/applied-soft-computing}{\underline{(Elsevier) Applied Soft Computing (IF=7.2, JCR Q1)}}}
      \item {\color{orange}\href{https://www.sciencedirect.com/journal/neural-networks}{\underline{(Elsevier) Neural Networks (IF=6.0, JCR Q1)}}}
      \item {\color{orange}\href{https://www.sciencedirect.com/journal/heliyon}{\underline{(Cell Press) Heliyon (IF=4.0, JCR Q1)}}}
      \item {\color{orange}\href{https://www.inderscience.com/jhome.php?jcode=ijbic}{\underline{(Inder Science) International Journal of Bio-Inspired Computation (IF=1.9, JCR Q2)}}}
      \item {\color{orange}\href{https://icsi2024.ustc.edu.cn/main.htm}{\underline{The International Conference on Sensing and Imaging (ICSI 2024)}}}
  \end{itemize}}
  
  % \subsection{\textcolor{lightblue}{COLLABORATING REVIEW ACTIVITIES}}
{\begin{itemize}[label=\textbullet] 
      \item {\color{orange}\href{https://www.techscience.com/journal/cmc}{\underline{(Tech Science Press) CMC-Computers Materials \& Continua (IF: 3.1, JCR Q3)}}}
      \item {\color{orange}\href{https://link.springer.com/journal/44196}{\underline{(Springer) International Journal of Computational Intelligence Systems (IF: 2.9, JCR Q3)}}}
      \item {\color{orange}\href{https://academic.oup.com/jcde}{\underline{(Oxford University Press) Journal of Computational Design and Engineering (IF: 3.1, JCR Q1)}}}
      \item {\color{orange}\href{https://www.mdpi.com/journal/mathematics}{\underline{(MDPI) Mathematics (IF=2.3, JCR Q1)}}}
      \item {\color{orange}\href{https://www.mdpi.com/journal/mathematics}{\underline{(MDPI) Applied Sciences (IF=2.5, JCR Q1)}}}
      \item {\color{orange}\href{https://www.mdpi.com/journal/biomimetics}{\underline{(MDPI) Biomimetics (IF=3.4, JCR Q1)}}}
      \item {\color{orange}\href{https://www.mdpi.com/journal/mathematics}{\underline{(MDPI) Symmetry (IF=2.2, JCR Q2)}}}
  \end{itemize}}
  
\section{Open-Source Projects and Tool Development}
- Artificial Visual System for Motion Direction Detection Modeled by Retina Neuro-scientific Knowledge. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]}\\
- Deep Neural Networks Coding for Motion Direction Detection. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- Wind Farm Layout Optimization Problem Benchmark Platform Coded by Matlab. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- Spherical Search Algorithm with Memory-guided Population Stage-Wise Control for Bound-Constrained Global Optimization Problem. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- Efficient Application of Level-Direction Guided Hierarchical Genetic Learning Particle Swarm Optimization for Wind Farm Layout Optimization Considering Landowners Behavior. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- Efficient Application of Potential-Unleashed High Performance Differential Evolution Algorithm for Wind Farm Layout Optimization. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- An Efficient Reconstructed Differential Evolution Variant by Some of the Current State-of-the-Art Strategies for CEC2024 Competition. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]} \\
- AI-powered model for predicting mortality risk in VA-ECMO patients: a multicenter cohort study. {\color{black}[\href{https://github.com/SichenTao}{\underline{Github}}]}


\section{Competences}
\begin{tabular}{>{\raggedright}p{5cm} p{15cm}}
% \textbf{COMPETENCES} & \\ \hline
\textbf{\textcolor{lightblue}{Computer skills}} & \textbf{Programming}: Python, Matlab, C++ \\
 & \textbf{AI-Frameworks}: Pytorch, Tensorflow, Keras, OpenCV, Scikit-Learn \\ 
 & \textbf{Operating systems}: Windows, Linux, MacOS \\
 % & \\
\textbf{\textcolor{lightblue}{Language}} & \textbf{English}: Basic \\
& \textbf{Japanese}: Japanese-Language Proficiency Test (JLPT) N2 Certificate \\
& \textbf{Chinese}: Native
\end{tabular}

\section{Extracurricular Activities}
Soccer, Running, Singing, Traveling, Computer Games

\section{}
Sichen Tao \\
Toyama, Japan \\
28/October/2025
 


% \section{Skills}
% {\begin{itemize}[label=\textbullet]
% \item {\textbf{Data Visualization:} Microsoft Power BI, Excel}
% \item {\textbf{Digital Marketing:} Project Management, Social Media Optimization, Content Writing, Campaign Analysis \& Reporting, PPC \& SEM Strategies, Conversion rate optimization (CRO), PPC advertising}
% \item {\textbf{Software:} Project (MSP), Adobe PhotoShop, Audition, Canva}
% \item {\textbf{SEO:} Google Search Console, Analytics, Looker Studio, Trends, Screaming Frog, SEMrush, Ahrefs, WordPress}
% \item {\textbf{Soft Skills:} Presentation, Planning, Organized, Creative Problem-Solving, Teamwork, Active Listening, Adaptability, Analytical Thinking}
% \end{itemize}}

% \section{Languages}
% \begin{multicols}{2}
%     \begin{itemize}[label=\textbullet]
%     \item \textbf{English} [Native]
%     \item {\textbf{French} [Basic] - Learning}
%     \item {\textbf{Spanish} [Native]}
%     \item {\textbf{German} [Basic] - A1}
%     \end{itemize}
% \end{multicols}
\end{document}
